openarchaeoCollaboration

### 2021-06-13 analysis/paper.Rmd
Add some tasks to do

@@

```{r plot-gh_langs, fig.show="hold", out.width="50%"}
oarch %>%
  unnest(gh_langs) %>%
  drop_na(lang, bytes) %>%
  group_by(lang) %>%
  summarise(n = n(), .groups = "drop") %>%
  arrange(-n) %>%
  slice(1:10) %>%
  ggplot(aes(fct_reorder(lang, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Repository languages",
       subtitle = "Number of repositories using top 10 languages",
       caption = "Data: open-archaeo.info and GitHub API",
       x = NULL, y = "Number of repositories")

@@

```{r plot-repo-hosts}
# TODO: add "none"
oarch %>% 
  pivot_longer(c(github, gitlab, bitbucket, launchpad, codeberg),
               names_to = "repo_host", values_to = "repo_url") %>% 
  drop_na(repo_url) %>% 
  count(repo_host) %>% 
  arrange(-n) %>%
  ggplot(aes(fct_reorder(repo_host, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Repository hosts",
       caption = "Data: open-archaeo.info",
       x = NULL, y = "Number of projects")
```
ZB note: How many users per platform? Codeberg is second but only has one user.

@@

@@

>>>>

TODO: colour by platform

@@

```{r plot-gh_langs, fig.show="hold", out.width="50%"}
# TODO: some merging of tags
# TODO: a crosstab/heatmap of tag combinations
oarch %>%
  unnest(gh_langs) %>%
  drop_na(lang, bytes) %>%
  group_by(lang) %>%
  summarise(n = n(), .groups = "drop") %>%
  arrange(-n) %>%
  slice(1:10) %>%
  ggplot(aes(fct_reorder(lang, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Repository languages",
       subtitle = "Number of repositories using top 10 languages",
       caption = "Data: open-archaeo.info and GitHub API",
       x = NULL, y = "Number of repositories")

@@

```{r plot-repo-hosts}
# TODO: add "none"
# TODO: version with unique authors
oarch %>% 
  pivot_longer(c(github, gitlab, bitbucket, launchpad, codeberg),
               names_to = "repo_host", values_to = "repo_url") %>% 
  drop_na(repo_url) %>% 
  count(repo_host) %>% 
  arrange(-n) %>%
  ggplot(aes(fct_reorder(repo_host, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Repository hosts",
       caption = "Data: open-archaeo.info",
       x = NULL, y = "Number of projects")
```
ZB note: How many users per platform? Codeberg is second but only has one user.

@@

TODO: barcode plot (see above)

@@

TODO: For this we need **covariaties**! Could be:

* Domain (tags and categories)
* Time
* Social aspects: e.g. centrality extracted from network analysis
